Network Configuration Synthesis with Abstract Topologies

### 2016-11-10 paper/abstraction/paper.tex
update pg pictures

\begin{figure*}[t!]
  \begin{minipage}[t]{.4\linewidth}
  \hdr{Policy Automata}{}
    \begin{tikzpicture}[>=stealth',shorten >=1pt,auto,node distance=2cm,minimum size=.5cm]
      \state{0}{$0$}{              }{}
      \state{1}{$1$}{right of=0}{accepting}
      \transition{0}{0}{out}{loop above}
      \transition{0}{1}{Peer1}{}
      \transition{1}{1}{in}{loop above}
      \node at (1,-1){Rank 1 DFA};
    \end{tikzpicture}
    ~~~~~
    \begin{tikzpicture}[>=stealth',shorten >=1pt,auto,node distance=2cm,minimum size=.5cm]
      \state{0}{$0$}{              }{}
      \state{1}{$1$}{right of=0}{accepting}
      \transition{0}{0}{out}{loop above}
      \transition{0}{1}{Peer2}{}
      \transition{1}{1}{in}{loop above}
      \node at (1,-1){Rank 2 DFA};
    \end{tikzpicture}%
  \end{minipage}
  %
  ~~~~~~
  %
  \begin{minipage}[t]{.3\linewidth}
    \hdr{Concrete Topology}{}
    \includegraphics[width=.7\columnwidth]{figures/topology-con}
  \end{minipage}%
  %
  \begin{minipage}[t]{.3\linewidth}
    \hdr{Abstract Topology}{}
    \includegraphics[width=.57\columnwidth]{figures/topology-abs}
  \end{minipage}%

  \vspace{1em}
  \begin{minipage}[t]{.6\linewidth}
    \hdr{Concrete Product Graph}{}
    \includegraphics[width=.9\columnwidth]{figures/pg-con}
  \end{minipage}%
  \begin{minipage}[t]{.4\linewidth}
  \hdr{Abstract Product Graph}{}
    \includegraphics[width=.9\columnwidth]{figures/pg-abs}

@@

The compiler performs the following to improve its performance.

\para{Z3 memoization}

Although the k-disjoint path analysis takes place over the Product Graph representation, which may differ from the topology (e.g., for non-shortest paths routing), each application of the inference rules from figure~\ref{fig:abstract-analysis} depends only on the topology. Therefore, we lazily apply the rules and cache the satisfiability and minimization calls to Z3 after their first use. Doing this significantly speeds up the failure safety analysis. Furthermore, the cached results can be shared across different prefixes, each of which may have a unique Product graph representation. In practice, this means that after performing the abstract analysis for one prefix, the analysis becomes essentially "free" for any subsequent prefixes.

\para{Fast Substitution}

Substitution after compiling a policy abstractly can be expensive since each router must substitute all template variables for each of its connected peers. In practice, because many routers often share the same concrete peers, memoizing the substitution function greatly improves performance.

@@

\begin{figure}[t!]
  \begin{center}
      \begin{tabular}{| l | c | c | c |}
      \hline
      \textbf{Topology} & \textbf{Fixed} & \textbf{Reachable} & \textbf{K-paths} \\ \hline
      Fattree~\cite{fattree} & & \cmark & \cmark  \\ \hline
      Facebook Fattree~\cite{facebook-fattree} & & \cmark & \cmark \\ \hline
      F10 Fattree~\cite{f10-fattree} & & \cmark & \cmark \\ \hline
      VL2 Fattree~\cite{vl2-fattree} & & & \\ \hline
      BCube~\cite{bcube} & $k$ & \cmark & \xmark \\ \hline
      DCell~\cite{dcell} & $k$ & \cmark & \xmark \\ \hline
         %& HCN & $h$ & \cmark & \xmark \\
      Butterfly~\cite{butterfly} & $n$ & \cmark & \cmark \\ \hline
      Hypercube & $N$ & \cmark & \cmark \\ \hline
      HyperX~\cite{hyperx} & $L$ & \cmark & \cmark \\ \hline
      \end{tabular}
  \end{center}
  \caption{Abstract Analysis Precision.}
  \label{fig:analysis-precision}
\end{figure}

>>>>

\begin{figure*}[t!]
  \begin{minipage}[t]{.4\linewidth}
  \hdr{Policy Automata}{}
  \vspace{1em}
    \begin{tikzpicture}[>=stealth',shorten >=1pt,auto,node distance=2cm,minimum size=.5cm]
      \state{0}{$0$}{              }{}
      \state{1}{$1$}{right of=0}{accepting}
      \transition{0}{0}{out}{loop above}
      \transition{0}{1}{Peer1}{}
      \transition{1}{1}{in}{loop above}
      \node at (1,-1){Rank 1 DFA};
    \end{tikzpicture}
    ~~~~~
    \begin{tikzpicture}[>=stealth',shorten >=1pt,auto,node distance=2cm,minimum size=.5cm]
      \state{0}{$0$}{              }{}
      \state{1}{$1$}{right of=0}{accepting}
      \transition{0}{0}{out}{loop above}
      \transition{0}{1}{Peer2}{}
      \transition{1}{1}{in}{loop above}
      \node at (1,-1){Rank 2 DFA};
    \end{tikzpicture}%
  \end{minipage}
  %
  ~~~~~~
  %
  \begin{minipage}[t]{.3\linewidth}
    \hdr{Concrete Topology}{}
    \vspace{1em}
    \includegraphics[width=.7\columnwidth]{figures/topology-con}
  \end{minipage}%
  %
  \begin{minipage}[t]{.3\linewidth}
    \hdr{Abstract Topology}{}
    \vspace{1em}
    \includegraphics[width=.57\columnwidth]{figures/topology-abs}
  \end{minipage}%

  \vspace{1em}
  \begin{minipage}[t]{.6\linewidth}
    \hdr{Concrete Product Graph}{}
    \includegraphics[width=.9\columnwidth]{figures/pg-con}
  \end{minipage}%
  \begin{minipage}[t]{.4\linewidth}
  \hdr{Abstract Product Graph}{}
    \includegraphics[width=.88\columnwidth]{figures/pg-abs}

@@

%The compiler performs the following to improve its performance.
%
%\para{Z3 memoization}

Although the disjoint path analysis takes place over the Product Graph, each application of the inference rules from figure~\ref{fig:inference-rules} depends only on the topology. Therefore, we lazily apply the rules and cache the satisfiability and minimization calls to $\nu$Z after their first use. Furthermore, the cached results are shared across different prefixes, each of which may have a unique Product graph representation.

%\para{Fast Substitution}
%
%Substitution after compiling a policy abstractly can be expensive since each router must substitute all template variables for each of its connected peers. In practice, because many routers often share the same concrete peers, memoizing the substitution function greatly improves performance.

@@

\begin{figure}[t!]
  \begin{center}
      \begin{tabular}{| l | c | c | c |}
      \hline
      \textbf{Topology} & \textbf{Fixed} & \textbf{Reachable} & \textbf{K-paths} \\ \hline
      Fattree~\cite{fattree} & & \cmark & \cmark  \\ \hline
      Facebook~\cite{facebook-fattree} & & \cmark & \cmark \\ \hline
      F10~\cite{f10-fattree} & & \cmark & \cmark \\ \hline
      VL2~\cite{vl2-fattree} & & & \\ \hline
      BCube~\cite{bcube} & $k$ & \cmark & \xmark \\ \hline
      DCell~\cite{dcell} & $k$ & \cmark & \xmark \\ \hline
         %& HCN & $h$ & \cmark & \xmark \\
      Butterfly~\cite{butterfly} & $n$ & \cmark & \cmark \\ \hline
      Hypercube & $N$ & \cmark & \cmark \\ \hline
      HyperX~\cite{hyperx} & $L$ & \cmark & \cmark \\ \hline
      \end{tabular}
  \end{center}
  \caption{Abstract Analysis Precision.}
  \label{fig:analysis-precision}
\end{figure}
